\titlespacing*{\section}{\parindent}{*4}{*0}

\begin{thebibliography}{17}
    \setlength{\leftskip}{-0.85cm}
    \setlength{\itemindent}{2.1cm}
    
    \bibitem{Abdul_Jamil:Speech Emotion Recognition} Badshah A.M., Abdul and Ahmad, Jamil and Rahim, Nasir and Baik, Sung. Speech Emotion Recognition from Spectrograms with Deep Convolutional Neural Network, 2017  

    \bibitem{Bogert_Healy:The Quefrency Alanysis} Bogert B.P., Healy M. J. R., and Tukey J. W., The Quefrency Alanysis of Time Series for Echoes: Cepstrum, Pseudo Autocovariance, Cross-Cepstrum and Saphe Cracking, Proceedings of the Symposium on Time Series Analysis (M. Rosenblatt, Ed) Chapter 15, 209-243. New York: Wiley, 1963

    \bibitem{Zdenek_Vlastimil:Acoustic_Attack_Using_Spectrogram_and_Neural_Network} Martinasek Z., Clupek V. Acoustic Attack on Keyboard Using Spectrogram and Neural Network, 2015

    \bibitem{Zhuang_Zhou:Keyboard_Acoustic_Emanations_revisited} Zhuang L., Zhou F., and Tygar J. D., Keyboard acoustic emanations revisited, in Proceedings of the 12th ACM conference on Computer and communications security, 2005

    \bibitem{Lloyd S: KMeans} Lloyd S.P. Least square quantization in PCM’s. Bell Telephone Laboratories Paper, 1957

    \bibitem{Steinhaus H: KMeans} Steinhaus H. Sur la division des corps materiels en parties. Bull. Acad. Polon. Sci., C1. III vol IV: 801—804., 1957

    \bibitem{Calinski  Harabas: cluster analysis} Calinski T., Harabasz J., A dendrite method for cluster analysis, Commu-nications in Statistics-theory and Methods 3 (1), 1974 1–27

    \bibitem{Peter J. Rousseeuw. Silhouettes} Rousseeuw P.J., Silhouettes: A graphical aid to the interpretation and validation of cluster analysis. Journal of Computational and Applied Mathematics, 1987

    \bibitem{Hinton G.E.:TSNE} van der Maaten L.J.P., Hinton G.E. Visualizing Data Using t-SNE // Journal of Machine Learning Research. — 2008. — November

    \bibitem{McInnes Healy:UMAP} McInnes L., John Healy, James Melville. UMAP: Uniform Manifold Appro-ximation and Projection for Dimension Reduction, 2018

    \bibitem{Dmitri_Asonov:Keyboard_Acoustic_Emanations} Asonov D., Rakesh A. Keyboard Acoustic Emanations, 2004

    \bibitem{Halevi-Saxena:Keyboard acoustic side channel attacks} Halevi T., Saxena N. Keyboard acoustic side channel attacks: exploring realistic and security-sensitive scenarios, 2014

    \bibitem{Au:Keyboard Acoustic Triangulation Attack} Hiu Yan F. Keyboard Acoustic Triangulation Attack BY Au, 2019

    \bibitem{Mikolov  Corrado: CBoW} Mikolov, T., Corrado, G., Chen K., Dean J. Efficient Estimation of Word Representations in Vector Space. Proceedings of the International Conference on Learning Representations (ICLR 2013), 1–12

    \bibitem{wiki_corpa}  Full-text corpus data -- https://www.corpusdata.org/wiki/samples/text.zip
   
    \bibitem{wordlist SCOWL} SCOWL (Spell Checker Oriented Word Lists) -- http://wordlist.aspell.net
   
    \bibitem{nlkt} NLTK (Natural Language Toolkit) -- https://www.nltk.org
    
\end{thebibliography}
